TBD

### 2021-02-24 outputs/paper/paper.Rmd
Update the format of tables

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####
### Format percent
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
### Format table for Chi-squared test
tableChisq <- function(capt, stat, df, p) {  
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p)
  chi_df <- data.frame(chi_stat, chi_param, paste(chi_p,"*"))

  kable(chi_df,
        digits = 2,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(symbol = "The Chi-squared statistic is significant at the 0.05 level")
}
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
kable(total,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)

>>>>

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####
### Format percent
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
### Format table for Chi-squared test
tableChisq <- function(capt, stat, df, p) {  
  chi_stat <- c(stat)
  chi_param <- c(df)
  chi_p <- c(p) %>%
    format(scientific=FALSE)

  if (chi_p < 0.05 & chi_p >= 0.01) {
    astr <- "*"
  } else if (chi_p < 0.01 & chi_p >= 0.001) {
    astr <- "**"
  } else if (chi_p < 0.001) {
    astr <- "***"
  } else {
    astr <- ""
  }

  chi_df <- data.frame(chi_stat, chi_param, paste(sprintf("%1.3f", as.numeric(chi_p)), astr))

  kable(chi_df,
        digits = 2,
        caption = capt,
        booktabs = T,
        col.names = c("X-squared",
                      "df",
                      "p-value")) %>%
    footnote(general = "* p < 0.05, ** p < 0.01, *** p < 0.001")
}
```

@@

```{r Q5 + Q6 Table, echo = FALSE, message = FALSE}
### Prior to (intervention start date), how many people did you employ?
### How many people do you currently employ?
t1 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(prior_employees = mean(Q5, na.rm = TRUE, .groups = NULL))
t2 <-
all_simulated_dataset %>%
  group_by(type) %>%
  summarise(curr_employees = mean(Q6, na.rm = TRUE), .groups = NULL)
total <- merge(t1, t2, by = c("type"))
kable(total,
      booktabs = T,
      col.names = c("Intervention Group",
                  "# of Employees Prior to Intervention",
                  "Current # of Employees")) %>%
      footnote(general = "Change in # of employees before and after intervention period (Q5 + Q6)") %>%
  kable_paper(c("striped", "hover"))
### T-Tests (Welch's)
#Q5
control_q5 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q5)
treatment_q5 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q5)
t3 <- t.test(control_q5, treatment_q5, paired = FALSE)
#Q6
control_q6 <-
  all_simulated_dataset %>%
  filter(type == "Control") %>%
  select(Q6)
treatment_q6 <-
  all_simulated_dataset %>%
  filter(type == "Treated") %>%
  select(Q6)
t4 <- t.test(control_q6, treatment_q6, paired = FALSE)
